Cartogram Mapping and Application to Cancer Data.

### 2019-06-14 review_article.Rmd
minor edits

Choropleth mapping methods explore a relationship across a geographical space, utilising administrative or other boundaries. In thematic maps colours or patterns are used represent levels, or rates, of the information communicated. @CIBMUK believes these 'representations are highly intuitive' as the familiar shapes help those looking at the maps to infer spatial relationships.  
They are true maps, used for visual inspection and can help to direct hypotheses about the statial patterns across the physical space. 
These true maps rely on visual perception, a fallible metric as it can 'weight the shades from the largest areas more heavily.' The inferences derived from visual inspection, and the hypotheses developed can suffer from 'bias'. The use of thematic disease mapping was motivated by a 'desire to evaluate geographical patterns' @DMAHP. This approach has been seen as a 'trigger for questions' which drives research of spatial distributions.  @MACM also recognises the intuition that can be derived from choropleths. However, his critique is that they must be 'validated by rigorous statistical analyses.'

@@

The data collection methods, and administrative control within regions lends itself to the presentation of cancer mortality rates across regions.

@@

General introduction:
Cartograms stepped toward this goal by highlighting areas of interest. Made some areas bigger on the map space, kept relationship with neighbours.
USA regular cartogram (UK too)

>>>>

Choropleth mapping methods explore a relationship across a geographical space, utilising administrative or other boundaries. In thematic maps colours, symbols or patterns are used represent levels, or rates, of the information communicated. @CIBMUK believes these 'representations are highly intuitive' as the familiar shapes help those looking at the maps to infer spatial relationships. 
They are true maps, used for visual inspection and can help to direct hypotheses about the statial patterns across the physical space. 
These true maps rely on visual perception, a fallible metric as it can 'weight the shades from the largest areas more heavily.' The inferences derived from visual inspection, and the hypotheses developed can suffer from 'bias'. The use of thematic disease mapping was motivated by a 'desire to evaluate geographical patterns' @DMAHP. This approach has been seen as a 'trigger for questions' which drives research of spatial distributions.  @MACM also recognises the intuition that can be derived from choropleths. However, his critique is that they must be 'validated by rigorous statistical analyses.'

@@

The data collection methods, and administrative control within regions lends itself to the presentation of cancer mortality rates across regions.
Data is now presented often age adjusted, and as relative rates of risk. Some also present changes in the rates

@@

General introduction:
Cartograms stepped toward this goal by highlighting areas of interest. Made some areas bigger on the map space, kept relationship with neighbours.
USA regular cartogram (UK too)
@DMAHP reduce the visual impact of large areas with small populations

distortion of spatial units -> proportional to the denominator variable. iso-demographic map, for approx equal population density.
